Estimated Annual Size of Claims Arising from Fire

### 2023-06-01 report/PAPER.tex
really finish

@@

% 此处填写摘要内容
\begin{abstract}
    The aim of this study is to construct a mathematical model based on Markov chains to predict \
    the total size of claims paid by insurers in the UK (and specifically England) due to fires in \
    the coming year. We split the regions of England into\ 
    \emph{"South West", "South East", "London", "East of England", "East Midlands", "Yorkshire and The Humber", "North West", "West Midlands", "North East"} \ 
    in order to obtain more refined predictions. First, we used house price data as a proxy for the \
    size of the claim per fire, assuming a fixed ratio of damage to the size of the claim per fire. \
    We then fitted the house price data with a log-normal distribution to obtain the distribution of \
    each claim size. Next, we modelled the number of fires using a Poisson distribution with a high \
    probability estimate. Finally, we use Monte Carlo simulations to estimate the size of the annual \
    fire loss. Our model takes into account two key factors, the number of fires and the size of claims \
    per fire, and provides insurers with an effective tool for predicting and managing fire insurance risk. \
    However, there are some assumptions and limitations to our model, such as our assumption of a fixed ratio \
    of losses to claim sizes per fire, which may not be entirely accurate in real life situations. \
    Future research could further improve this model to increase its predictive accuracy and usefulness. \\
    All data is taken from GOV.UK, the official website of the UK government.\\

@@

Our prediction process is twofold. First, we use the ARIMA model to forecast key parameters, including the frequency of fires, the loss per fire, and the ratio of losses to claims, among others. Our forecasting results are detailed in Table \ref{tb:pred}.

@@

@@

@@

\begin{subappendices}  % 附录环境

\section{Appendix A: Further on \LaTeX}
To clarify the importance of using \LaTeX\ in MCM or ICM, several points need to be covered, which are \ldots

To be more specific, \ldots

All in all, \ldots

Anyway, nobody \textbf{really} needs such appendix \ldots

\section{Appendix B: Program Codes}
Here are the program codes we used in our research.

% 代码环境示例三则
% 如您的论文不需要展示代码，请删除
% 更多用法，请参考 listings 宏包文档

% Python 代码示例
\begin{lstlisting}[language=Python, name={test.py}]
# Python code example
for i in range(10):
    print('Hello, world!')
\end{lstlisting}

% MATLAB 代码示例
\begin{lstlisting}[language=MATLAB, name={test.m}]
% MATLAB code example
for i = 1:10
    disp("hello, world!");
end
\end{lstlisting}

% C++ 代码示例
\begin{lstlisting}[language=C++, name={test.cpp}]
// C++ code example
#include <iostream>
using namespace std;

int main() {
    for (int i = 0; i < 10; i++)
        cout << "hello, world" << endl;
    return 0;
}
\end{lstlisting}

\end{subappendices}  % 附录内容结束

\end{document}  % 结束
% 三线表示例
% \begin{table}[!htbp]
% \begin{center}
% \caption{Notations}
% \begin{tabular}{cl}
%     \toprule
%     \multicolumn{1}{m{3cm}}{\centering Year}
%     &\multicolumn{1}{m{8cm}}{\centering Consumer Prices Index}
%     \\
%     \midrule
%     $2011$ &    {\centering 93.4}\\
%     $2012$ &96.1\\
%     $2013$ &98.5\\
%     $2014$ &100.0\\
%     $2015$ &100.0\\
%     $2016$ &100.7\\
%     $2017$ &103.4\\
%     $2018$ &105.9\\
%     $2019$ &107.8\\
%     $2020$ &108.7\\
%     $2021$ &111.6\\
%     $2022$ &121.7\\
%     \bottomrule
% \end{tabular}\label{tb:CPI}
% \end{center}
% \end{table}

>>>>

\usepackage{hyperref}
\hypersetup{hidelinks,
	colorlinks=true,
	allcolors=black,
	pdfstartview=Fit,
	breaklinks=true}

@@

% 此处填写摘要内容
\begin{abstract}
    The aim of this study is to construct a mathematical model based on Markov chains to predict \
    the total size of claims paid by insurers in the UK (and specifically England) due to fires in \
    the coming year. We split the regions of England into\ 
    \emph{"South West", "South East", "London", "East of England", "East Midlands", "Yorkshire and The Humber", "North West", "West Midlands", "North East"} \ 
    in order to obtain more refined predictions. First, we used house price data as a proxy for the \
    size of the claim per fire, assuming a fixed ratio of damage to the size of the claim per fire. \
    We then fitted the house price data with a log-normal distribution to obtain the distribution of \
    each claim size. Next, we modelled the number of fires using a Poisson distribution with a high \
    probability estimate. Finally, we use Monte Carlo simulations to estimate the size of the annual \
    fire loss. Our model takes into account two key factors, the number of fires and the size of claims \
    per fire, and provides insurers with an effective tool for predicting and managing fire insurance risk. \
    However, there are some assumptions and limitations to our model, such as our assumption of a fixed ratio \
    of losses to claim sizes per fire, which may not be entirely accurate in real life situations. \
    Future research could further improve this model to increase its predictive accuracy and usefulness. \\
    All data is taken from GOV.UK, the official website of the UK government.\\
    All Source code you can found in my \href{https://github.com/JavaZeroo/markov\_project}{Github: https://github.com/JavaZeroo/markov\_project}

@@

Our prediction process is twofold. First, we use the ARIMA model to forecast key parameters, including the frequency of fires, the loss per fire, and the ratio of losses to claims, among others. Our forecasting results are detailed in Table \ref{tb:pred}.The final predicted distribution of fire claim amounts for 2023 can be seen in Figure (\ref{fig:pred})

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{pred.jpg}
    \caption{This image shows the distribution of claim amounts by region}\label{fig:pred}
\end{figure}

@@

Our proposed model provides an innovative approach to estimating and predicting annual fire insurance claims. By using different models for different components of the process, we are able to exert greater control over the various factors influencing fire-related insurance claims. In addition, the model provides a commendable degree of explanatory power in relation to the annual cost of fires.

However, we recognise the inherent limitations. A number of assumptions have been made in constructing the model, which may limit its ability to capture every real world scenario. As a result, there may be some degree of discrepancy between the model's estimates and actual figures.

We therefore believe that there is ample scope for further research, in particular to refine the estimates of the proportion of residential fires and the corresponding loss ratio. This nuanced approach would contribute to a more accurate and robust model, thereby enhancing its utility in predicting fire-related insurance claims.

In conclusion, our model, while not without its limitations, represents a significant step forward in the field of predicting fire-related insurance claims. Further refinement, guided by real-world data and subsequent validation, would undoubtedly contribute to the evolution of this predictive model.

@@

% \begin{subappendices}  % 附录环境

% \section{Appendix A: Further on \LaTeX}
% To clarify the importance of using \LaTeX\ in MCM or ICM, several points need to be covered, which are \ldots

% To be more specific, \ldots

% All in all, \ldots

% Anyway, nobody \textbf{really} needs such appendix \ldots

% \section{Appendix B: Program Codes}
% Here are the program codes we used in our research.

% % 代码环境示例三则
% % 如您的论文不需要展示代码，请删除
% % 更多用法，请参考 listings 宏包文档

% % Python 代码示例
% \begin{lstlisting}[language=Python, name={test.py}]
% # Python code example
% for i in range(10):
%     print('Hello, world!')
% \end{lstlisting}

% % MATLAB 代码示例
% \begin{lstlisting}[language=MATLAB, name={test.m}]
% % MATLAB code example
% for i = 1:10
%     disp("hello, world!");
% end
% \end{lstlisting}

% % C++ 代码示例
% \begin{lstlisting}[language=C++, name={test.cpp}]
% // C++ code example
% #include <iostream>
% using namespace std;

% int main() {
%     for (int i = 0; i < 10; i++)
%         cout << "hello, world" << endl;
%     return 0;
% }
% \end{lstlisting}

% \end{subappendices}  % 附录内容结束

\end{document}  % 结束
